%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Dailymealz} % Organization
    {Riyadh, Saudi Arabia} % Location
    {Dec. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team of 5 developers in implementing a background location check-in system for the driver app, improving route efficiency by 25\%.}
        \item {Collaborated with cross-functional teams to ensure seamless integration of third-party tools, resulting in an enhanced user experience and reduced downtime.}
        \item {Built automated build pipeline on App Center for direct store deployment and internal testing, which reduce time to market by 80\%.}
        \item {Increased system Observability by adding monitors on main flows using Datadog and OpenTelemetry stack, which contributed to decrease Mean Time To Resolve by 30\%.}
        \item {Implemented a centralized module to track analytical events that make use of Observer Pattern and handle all integrated analytics events.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-Stack Developer} % Job title
    {Nformacy.} % Organization
    {Cairo, Egypt} % Location
    {Oct. 2020 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led development from business requirements to deployment, including backend and frontend.}
        \item {Designed and implemented automated BDD tests using Cypress, improving test coverage by more than 70\%.}
        \item {Migrated existing web applications to support the SaaS model which enhanced the product to be more market fit.}
        \item {Implemented an internal calendar system for mentor availability and
customer booking.}
        \item {Ensured interoperability with third-party applications (Zoom,
ClickUp, calendar)}
        \item {Managed cloud infrastructure and deployment pipelines}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {DevSquads} % Organization
    {Cairo, Egypt} % Location
    {Aug. 2018 - Oct. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked in a self-organizing team to build high-quality software using Extreme Programming principles.}
        \item {Developed across multiple platforms: React Native for mobile, Ruby on Rails, Java Spring for backend, and React for frontend.}
        \item {Mentored teams in adopting Extreme Programming (XP) and Agile practices, resulting in a 30\% increase in delivery efficiency and a significant reduction in technical debt.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Fikr Labs.} % Organization
    {Cairo, Egypt} % Location
    {Jan. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed software using TDD with evolutionary design.}
        \item {Delivered thin vertical slice delivery on many projects across
multiple stacks: Java, React Native, React.js.}
        \item {Maintained and refactored legacy code base using automated tests which provide a safety net and enhanced quality.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
